\chapter{Security Engineering}'

\section{Usability and Pshycology}

	\begin{itemize}
		\item Authentication vs Identification
		\item Why do I as a developer want to add insecure code?
		\item Pretexting
		\item Phishing
		\item What does the brain do better than a computer?
		\item What does a computer do better than the brain?
		\item How do people act under under uncertainty?
		\item Social psychology - Authority
		\item Humans memory and password policy
		\item What is social engineering?
		\item Eavesdropping ("avlytting")
		\item CAPTHA
	\end{itemize}

\clearpage
\section{Protocols}
	\begin{itemize}
		\item Simple authentication vs. Two-factor authentication
		\item Basic key management
		\item Needham-Schroeder protocol
		\item Kerberos
		\item BAN logic (not in details, but know what it is)
	\end{itemize}

\section{Access Control}
	\begin{itemize}
		\item What is access control?
		\item Access Control Lists (ACL)
		\item Capabilities
		\item Groups vs. roles in (access system)
		\item Sandboxing
		\item Proof carrying code
	\end{itemize}

\section{Cryptography}
	\begin{itemize}
		\item One-way function
	\end{itemize}

\clearpage
\section{Multilevel security}
	\begin{itemize}
		\item What is a security model?
		\item Bell LaPadula security model
		\item The simple security property
		\item Classification levels
		\item MAC (Mandatory Acces Control) vs DAC (Discretionary Access Control)
		\item High/low-water-mark
		\item The Biba model
		\item (No) Write up/down and (No) read up/down
	\end{itemize}

\section{Multilateral Security}
	\begin{itemize}
		\item Multilevel security vs Multilateral security
		\item The lattice model
		\item The Chineese wall
	\end{itemize}
